Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-22 documents/mixtures/mixture_models.tex
last paragraphs

% to-do
% -----
% - HOGG: can we drop the regularization in the badness and still succeeed?  If so, let's do that (and drop it in the text).
% - DSTN: make figures showing use of the models in a real situation; see last figure
% - HOGG: does the Lupton paper give the profiles, or should we cite the code directly?
% - make sure the technical issues about convolution and interpolation don't exist *only* in the figure caption
% - HOGG: need Bundy reference
% - HOGG: make what I say about M=6 lux and M=8 lux true -- ie, edit the Tractor code!
% - send to Jim Bosch and Kevin Bundy for comments

@@

In our work on \project{The Tractor}, we use the $M^{\lux}=6$ lux and
the $M^{\luv}=8$ luv profiles.  Our advice to users would be to do the
same.  We use the lux and luv over the exp and dev partly because of
their better behaviors numerically, and partly because they and we are
both part of the \project{SDSS} tradition.  These---$M^{\lux}=6$ and
$M^{\luv}=8$ are good compromises between mixture complexity ($M$) and
quality of fit.  Also, even the best-fitting late-type and early-type
galaxies deviate from exponential and de~Vaucouleurs fits by more than
do these high-quality mixture-of-Gaussian approxmations; no precision
is lost.

@@

... what about mixtures of exps and devs:  No problem!...

... finally: The insights that \emph{could} be gained by interrogating
these profile approximations in three dimensions...!

>>>>

% to-do
% -----
% - HOGG: can we drop the regularization in the badness and still succeeed?  If so, let's do that (and drop it in the text).
% - DSTN: make figures showing use of the models in a real situation; see last figure
% - HOGG: does the Lupton paper give the profiles, or should we cite the code directly?
% - HOGG: need Bundy reference
% - HOGG: make what I say about M=6 lux and M=8 lux true -- ie, edit the Tractor code!
% - HOGG: send to Lupton and Bundy for comments
% - DSTN: can we be more specific about how Bosch is using them? I would like to cite users.
% - DSTN: is there anyone we need to ack on your side, or granting agencies?
% - HOGG: should we make Machine Readable Tables for PASP?

@@

In our work on \project{The Tractor}, we use the $M^{\lux}=6$ lux and
the $M^{\luv}=8$ luv profiles.  Our advice to users would be to do the
same.  We use the lux and luv over the exp and dev partly because of
their better behaviors numerically, and partly because they and we are
both part of the \project{SDSS} tradition.  These---$M^{\lux}=6$ and
$M^{\luv}=8$---are good compromises between mixture complexity ($M$)
and quality of fit (badness).  Also, even the best-fitting late-type
and early-type galaxies deviate from exponential and de~Vaucouleurs
fits by more than do these high-quality mixture-of-Gaussian
approxmations; no precision is lost.

@@

In the \project{SDSS}, \project{GALFIT}, and much of our own work, the
models that are fit are (effectively) mixtures of exp and dev or exp
and ser or lux and luv profiles.  Mixtures of profiles that are each
themselves mixtures of Gaussians are no harder to render than either
profile separately.  There is some book-keeping, of course, because
each component gets affine-transformed separately before they are both
PSF-convolved.

One amusing aspect of mixture-of-Gaussian profiles has to do with
projection from three to two dimensions.  The projection of a
three-dimensional Gaussian is a two-dimensional Gaussian; the
two-dimensional, rigid, circular approximations we have made for the
ser profiles can be deprojected to rigid, spherical approximations to
the three-dimensional profiles trivially.  The two-dimensional models
we have started with are not accurate models of galaxies in
detail---no galaxy follows exactly any ser profile---so deprojection
of our approximations are are not that interesting in themselves.
However, the general program of fitting two-dimensional sources with
mixtures of Gaussians may have strong implications in the future for
three-dimensional modeling and deprojection.
